Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-19 fmics/paper.tex
Add HOL4 and Isabelle bibliography entries

The formal verification effort described in this paper is based on
 the use of mechanised logical deduction, or theorem proving, to
 demonstrate that desired properties of a system are logically implied
 by a formal model of the system.  Our approach to theorem-proving
 uses the HOL4 open source software tool, which was developed
 initially at the University of Cambridge, but now by an international
 team~\cite{HOL4}.  HOL4 partially automates the task of proving theorems of
 higher-order logic [ref], a formal logic with a similar expressive
 power to set theory that is widely used for formalising hardware and
 software models and statements about them.  Typically, a very large
 portion of the logical deduction is performed automatically by the
 HOL4 system leaving the user to provide the high level proof
 strategy.  The implementation of the HOL4 system is based on Milner's
 LCF approach [ref] and consists of a small “kernel” that provides a
 very high level of confidence in the logical soundness of the
 verification results obtained using the system. The work described
 here could have been done using other systems such as HOL Light
 [ref], Isabelle/HOL [ref], ProofPower [ref], PVS [ref] or Coq
 [ref]. The first three of these support essentially the same version
 of higher-order logic as HOL4, whilst PVS and Coq support more
 powerful logics. <What about ACL2?>

>>>>

The formal verification effort described in this paper is based on
 the use of mechanised logical deduction, or theorem proving, to
 demonstrate that desired properties of a system are logically implied
 by a formal model of the system.  Our approach to theorem-proving
 uses the HOL4 open source software tool, which was developed
 initially at the University of Cambridge, but now by an international
 team~\cite{HOL4}.  HOL4 partially automates the task of proving theorems of
 higher-order logic [ref], a formal logic with a similar expressive
 power to set theory that is widely used for formalising hardware and
 software models and statements about them.  Typically, a very large
 portion of the logical deduction is performed automatically by the
 HOL4 system leaving the user to provide the high level proof
 strategy.  The implementation of the HOL4 system is based on Milner's
 LCF approach [ref] and consists of a small “kernel” that provides a
 very high level of confidence in the logical soundness of the
 verification results obtained using the system. The work described
 here could have been done using other systems such as HOL Light
 [ref], Isabelle/HOL~\cite{Isabelle}, ProofPower [ref], PVS [ref] or Coq
 [ref]. The first three of these support essentially the same version
 of higher-order logic as HOL4, whilst PVS and Coq support more
 powerful logics. <What about ACL2?>
